---
title: "Exploring_Leaving_multiCol"
author: "Callum Simpson"
date: "24/11/2020"
output: html_document
---

```{r setup, include=FALSE}

setwd("~/CSC8631_202021")

library('ProjectTemplate')
load.project()


```

## Anylsis of multipale colunms 

This document contains deeper dive into my now cleaned data (combine_Leaving_clean) to see what results I get when I look at multiple variables at the same time.
This is so that I could get a better understanding of patterns and correlations in the data


## The reason why a person left the course and there last completed step

In our last set of analysis we found that there was alot of people who left the course with out completing any step (under the assumtion that all NA values are actually not completed a week).



```{r reasonleft_lastComp}

combine_Leaving_clean_v2

ggplot(combine_Leaving_clean_v2, aes(leaving_reason)) + geom_bar() + 
  coord_flip() + ggtitle("The reason why people left") + facet_wrap(~ last_completed_week_number)


```

