---
title: "Report"
author: "Callum Simpson"
date: "01/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
# Knitr setup
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```


```{r include=FALSE}
# Load project

library('ProjectTemplate')
load.project()

source("src/SC_for_merged_analysis.R")
source("src/SC_for_leaver_analysis.R")
source("src/SC_for_clean_enroled.R")
source("src/SC_for_clean_leaving_data.R")

```


# CSC8631 202021 Report
## By Callum Matthew Simspon
## b6030326

The following is my report of my analysis CSC8631 - Data Management and Exploratory Data Analysis course work. It will discuss my analysis and how I did it using the Crisp-DM model.


## Business understanding

As the first step in the Crisp-DM model is business understanding I first looked into the task that I had been given and who gave it was for.

### The Client background 

The cilent for this report will be Newcastle University who is using the site FutureLearn to host a course on Cyber Security: Safety at Home, Online, in Life. FutureLearn is an online training provider offering a wide selection of courses, often delivered in association with big-name colleges. Newcastle University is a UK public research university based in Newcastle upon Tyne

### The objective 

Newcastle university has gathered information about the users that have attended this course and are wanting to perform learning Analytics on this data to get insight into student engagement.

Learning Analytics is a rapidly-growing application area for Data Science, defined as “the measurement, collection, analysis and reporting of data about learners and their contexts, for purposes of understanding and optimizing learning and the environment in which it occurs”

As there is no formal requirement on the question that the university wants to be investiagted I decided that I wanted to get a better understanding of why a user leaves the course. I feel like this would be a good measure of engagement as I could potentially find common reason and trends that are causing to leave the course meaning my findings could help improve the course to keep users engaded and lower the amount of people that leave the course. 

Because of this my business object will be "give useful insights into why people decide to leave the course"

### Assess situation 

I have been given data about the users who have attended the course, like enrollment data and answers to activity question. The data is split across seven run of the course (so each run has it own set of user data).  

### Determine data mining goals

As i am want to look into useful insights into why people decide to leave the course a clear data mining goal will be finding out the common reason a person leaves so that the course be updated to help reduce people leaving in the next cycle. Similarly another goal of mine should be be finding out who is leaving as again it means that measure could be put in check to increase engagement in that group. My success criteria will be data that clearly allows us to see why people are leaving. 

### Project plan

My aim is to 

- understand data by the 17th of November
- have the first clean bit of data by the 22nd of November 
- Have roughly two weeks to do my analysis 
- get my analysis done by the 1st of December.  

I am planning to use and R project with a project template to ensure that my code can be reproducible
