---
title: "CSC8631_202021_Explore"
author: "Callum Simpson"
date: "20/11/2020"
output: html_document
---

```{r setup, include=FALSE}

setwd("CSC8631_202021")

library('ProjectTemplate')
load.project()


```

## Set up

This is an R Markdown which devels into me geeting a grips with the data, what exactly that it is telling us so that i could find an area in which to create a question

Im using this document to spit ball ideas and to make sure that my project has been created correctly


## Archetype survey responses

Week 3 - 7  

Seems to be a collection of the archetypes of the users.

```{r the_data}

head(cyber_security_3_archetype_survey_responses)

table(cyber_security_3_archetype_survey_responses$archetype)

head(cyber_security_4_archetype_survey_responses)

head(cyber_security_5_archetype_survey_responses)

head(cyber_security_6_archetype_survey_responses)

head(cyber_security_7_archetype_survey_responses)
```
## cyber security enrolments

The enrolments for each run 

contianes 
- role of the person
- gender
- country 
- age
- highest education
- If they are employed and where 


```{r the_data}

head(cyber_security_1_enrolments)
head(cyber_security_2_enrolments)
head(cyber_security_3_enrolments)
head(cyber_security_4_enrolments)
head(cyber_security_5_enrolments)
head(cyber_security_6_enrolments)
head(cyber_security_7_enrolments)

```

## cyber leaving results

weeks 4 - 6

The reason people left and when about in the course they left


```{r the_data}

head(cyber_security_4_leaving_survey_responses)
head(cyber_security_5_leaving_survey_responses)
head(cyber_security_6_leaving_survey_responses)
head(cyber_security_7_leaving_survey_responses)

```

## question response

All weeks 

The responses for the questions for that cycle

```{r the_data}

head(cyber_security_1_question_response)
head(cyber_security_2_question_response)
head(cyber_security_3_question_response)
head(cyber_security_4_question_response)
head(cyber_security_5_question_response)
head(cyber_security_6_question_response)
head(cyber_security_7_question_response)

```

## Step activity

Each steps and when people started and finished the step


```{r the_data}

head(cyber_security_1_step_activity)

```


## Team members

2-7 

Each steps and when people started and finished the step

- team role is the role whole of the person in the team
- user role seems to be role of what the user 

```{r the_data}

head(cyber_security_3_team_members)

```


##weekly_sentiment_survey_responses

Seems to be only week 6 and 7

Peoples response to the course but only seems to weeks 6 and 7


```{r the_data}

head(cyber_security_6_weekly_sentiment_survey_responses)

```

##video_stats

Information about the videos

how long people are watching 
where they are watching it 
what people are watching it on


```{r the_data}

head(cyber_security_3_video_stats)

```